---
title: "Final_Project"
author: "Karim Kidiss & Carine Lemaire"
date: "19 mars 2017"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    theme: readable
    highlight: pygments
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description of the problem

The dataset we will analyze in this final project is about the Titanic and contains elements such as the passenger name and id, their gender, their age etc. And we wanted to analyze this data because some questions were raised and also to test our theory which is : Do some factors affect the survivability chance of the people on board ? 


```{r}
data = read.csv("Titanic.csv")
```

## Description of the dataset and the questions 

Some interesting questions that deserve answering : 
What attribute affects the survivability of the people on board ? Which one can we conclude on that it is the main factor ? 

Willing to answer these questions we will dive in the dataset and analyze it :

```{r pressure, echo=FALSE}
summary(data)
```

