---
title: "Final_Project"
author: "Karim Kidiss & Carine Lemaire"
date: "19 mars 2017"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    theme: readable
    highlight: pygments
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description of the problem

The dataset we will analyze in this final project is about the Titanic and contains elements such as the passenger name and id, their gender, their age and wether they survived or not etc. And we wanted to analyze this data because some questions were raised and also to test our theory which is : Do some factors affect the survivability chance of the people on board ? 


```{r}
data = read.csv("Titanic.csv")
```

## Description of the dataset and the questions 

Some interesting questions that deserve answering : 
What attribute affects the survivability of the people on board ? Which one can we conclude on that it is the main factor ? 

Willing to answer these questions we will dive in the dataset and analyze it :

```{r}
summary(data)
```

## Logistic Regression

The logistic regression is a predictive analysis, it is used to describe data and to explain the relationship between one dependant binary variable which in our case is the survivability ( wether the person survived or not ) and other variables we have in our dataset.
We will study the dataset with a logistic regression to find the attributes which affect the survivability of the people on board. 

```{r logistic regression a}
library(caTools)
set.seed(123)
split = sample.split(data$Survived, SplitRatio = 0.75)
training_set = subset(data, split == TRUE)
test_set = subset(data, split == FALSE)
```

We will do a logistic regression model of Survived in function of Age.

```{r logistic regression b}
classifier <- glm(Survived ~ Age, family = binomial, data=training_set)
summary(classifier)
```

We can see the p-value is greater than 0,05, so we can conclude that Age is not a significant factor in the survivability.

Now we can plot it using the ggplot2 library which gives us better visuals 

```{r}
library(ggplot2)
ggplot(training_set, aes(x=Age, y=Survived)) + geom_point() + stat_smooth(method = "glm", method.args = list(family ="binomial"), se=FALSE)
plot(training_set$Age, training_set$Survived)
curve(predict(classifier, data.frame(Age=x), type='response'), add=TRUE)
```

We can chose an other predict with Age, Sex and Pclass

```{r logistic regression c}
library(caTools)
set.seed(123)
split = sample.split(data$Survived, SplitRatio = 0.75)
training_set = subset(data, split == TRUE)
test_set = subset(data, split == FALSE)
classifier <- glm(Survived ~ Age + Sex + Pclass , family = binomial, data=training_set)
summary(classifier)
```

Now the p-value is lower than 0,05 so the predict (Sex, Age and Pclass) is significant.

We can do a confusion matrix to evaluate the predictions.

```{r logistic regression d}
pred=predict(classifier,training_set,type='response')
mat<-ifelse(pred>0.5,1,0)
#Pclass
table(mat,training_set[,3])
#Sex
table(mat,training_set[,5])
#Age : 0 for people<40, else 1
t=ifelse(training_set[,6]>40,1,0)
table(mat,t)
```

With this model, we can see that more women survived than men. It's the same case for young people. Moreover, there is no difference between the class of the people.


## Linear Discriminant Analysis

Now, we will do a LDA model of Survived in function of Age and Sex.

```{r Linear Discriminant Analysis a}
library(MASS)
classifier.lda <- lda(Survived~Age+Sex, data=training_set)
classifier.lda
```
```{r Linear Discriminant Analysis daaa}
classifier.lda$prior
```
This shows only 38% people survived.

```{r Linear Discriminant Analysis aaa}
classifier.lda$means
```

We can see the most people who didn't survive are men (85%)

```{r Linear Discriminant Analysis vaaa}
pred_lda=predict(classifier.lda,test_set[c(5,6)],type='response')
str(pred_lda)
```

We can compute a confusion matrix :

```{r Linear Discriminant Analysis b}
y_pred<-ifelse(pred>0.5,1,0)
y=y_pred[1:223]

table(pred_lda$class,y)
```

##Conclusion
With this two methods we showed people who have survived are in majority women or young.